17th International Satisfiability Modulo Theories Competition (SMT-COMP 2022): Rules and Procedures

### 2022-06-21 rules/rules22.tex
update link
fix

\header{SMT Solver.}
%
A Satisfiability Modulo Theories (SMT) solver that can enter SMT-COMP is a tool that can determine the
(un)satisfia\-bility of benchmarks from the SMT-LIB benchmark library
(\url{http://www.smt-lib.org/benchmarks.shtml}).

@@

\header{Participation in the Competition.}
%
For participation in SMT-COMP, a solver must be uploaded to StarExec
and made publicly available, or communicated separately to the
organisers for the \cloudtrack{} and \paralleltrack{}.  StarExec supports solver configurations;
for clarity, \emph{each submitted solver must have one configuration
  only}.  Moreover, the organizers must be informed of the solver's
presence \emph{and the tracks and divisions which it enters} via the
web form at
\begin{center}
  \url{https://forms.gle/9Eged2txtvJxGXeD9}
\end{center}
For each track the submission must specify the logics which are
supported by the solver.  The solver will enter all divisions where it
supports at least one logic.  A submission \textbf{must} also include a
link to the \emph{system description} (see below) and a \emph{32-bit
  unsigned integer}.  These integer numbers, collected from all
submissions, are used to seed competition tools.

>>>>

\header{SMT Solver.}
%
A Satisfiability Modulo Theories (SMT) solver that can enter SMT-COMP is a tool that can determine the
(un)satisfia\-bility of benchmarks from the SMT-LIB benchmark library
(\url{https://smtlib.cs.uiowa.edu/benchmarks.shtml}).

@@

\header{Participation in the Competition.}
%
For participation in SMT-COMP, a solver must be uploaded to StarExec
and made publicly available, or communicated separately to the
organisers for the \cloudtrack{} and \paralleltrack{}.  StarExec supports solver configurations;
for clarity, \emph{each submitted solver must have one configuration
  only}.  Moreover, the organizers must be informed of the solver's
presence \emph{and the tracks and divisions which it enters} via the
web form at
\begin{center}
  \url{https://forms.gle/ewNQdFJbmQ12GxpX8}
\end{center}
For each track the submission must specify the logics which are
supported by the solver.  The solver will enter all divisions where it
supports at least one logic.  A submission \textbf{must} also include a
link to the \emph{system description} (see below) and a \emph{32-bit
  unsigned integer}.  These integer numbers, collected from all
submissions, are used to seed competition tools.
